---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hgnc <img src='man/figures/logo.svg' align="right" height="139" />

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/hgnc)](https://CRAN.R-project.org/package=hgnc)
[![R-CMD-check](https://github.com/patterninstitute/hgnc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/patterninstitute/hgnc/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `{hgnc}` is to easily import [Human Gene
Nomenclature](https://www.genenames.org) into R.

## Installation

Install `{hgnc}` from CRAN:

``` r
install.packages("hgnc")
```

## Usage

To import the latest HGNC gene data set in tabular format directly into memory
as a tibble do as follows:

```{r}
library(hgnc)

# Check the date of HGNC last update
last_update()

# Import the data set in tidy tabular format
(hgnc_dataset <- import_hgnc_dataset())
```

## Learn more

Learn more about this package by reading the documentation at
<https://www.pattern.institute/hgnc/>.

## Citing the HGNC

To cite HGNC nomenclature resources use:

- Tweedie S, Braschi B, Gray KA, Jones TEM, Seal RL, Yates B, Bruford EA. _Genenames.org: the HGNC and VGNC resources in 2021._ Nucleic Acids Res. 49, D939--D946 (2021). doi: [10.1093/nar/gkaa980](https://doi.org/10.1093/nar/gkaa980)

To cite data within the database use the following format:
 
- HGNC Database, HUGO Gene Nomenclature Committee (HGNC), European Molecular Biology Laboratory, European Bioinformatics Institute (EMBL-EBI), Wellcome Genome Campus, Hinxton, Cambridge CB10 1SD, United Kingdom www.genenames.org. 

Please include the month and year you retrieved the data cited.
