---
title: "Import Human Gene Nomenclature"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(hgnc)
```

The [HUGO Gene Nomenclature Committee (HGNC)](https://www.genenames.org/) is a
committee of the Human Genome Organisation (HUGO) that sets the standards for
human gene nomenclature.

The HGNC approves a unique and meaningful name for every known human gene, based
on a group of experts. In addition, the HGNC also provides the mapping between
gene symbols to gene entries in other popular databases or resources: the HGNC
complete gene set.

Use the function `import_hgnc_dataset()` to import the latest HGNC complete
gene data set directly into R. This downloads the latest archive from
<https://www.genenames.org/download/archive/monthly/tsv/>.

```{r}
(hgnc_dataset <- import_hgnc_dataset())
```

## Saving to disk

`import_hgnc_dataset()` reads data directly into memory. Use
`download_hgnc_dataset()` to save data into disk first, and import straightaway
from disk:

```{r}
# Note that `download_hgnc_dataset()` returns the path of the saved file.
(local_file <- download_hgnc_dataset())
import_hgnc_dataset(file = local_file)
```

## Data releases

HGNC complete gene data sets are released monthly and quarterly. If you prefer
to download a specific release other than the latest, use first the function
`list_archives()` to list available archives:

```{r}
(releases <- list_archives("monthly"))
```

Then pass the URL corresponding to the archive of interest to
`import_hgnc_dataset()`:

```{r warning=FALSE}
# First release, 2021 March 01
(url <- releases$url[1])
import_hgnc_dataset(file = url)
```

