---
title: "Crosswalk across identifiers"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(hgnc)
```

Besides providing a name for every human gene, the _HGNC complete gene
set_[^import] also includes mappings of HGNC symbols to gene entries in other
popular databases or resources, e.g. to Entrez gene or UCSC gene identifiers.

[^import]: See `vignette("import")` for details on how to import this data
set.

The helper `crosswalk()` provides an easy interface to crosswalk (i.e. map or
translate) across identifiers. This function allows matching exact terms in
columns of an imported HGNC complete gene set and return values from another
column.

#### Gene symbol to HUGO identifier and back

  ```{r}
  # Example bundled data set.
  hgnc_dt <- hgnc_dataset_example()
  
  # From gene symbol to HUGO identifier
  crosswalk(
    c("A1BG", "A1BG-AS1"),
    from = "symbol",
    to = "hgnc_id",
    hgnc_dataset = hgnc_dt
  )
  
  # and back.
  crosswalk(
    c("HGNC:5", "HGNC:37133"),
    from = "hgnc_id",
    to = "symbol",
    hgnc_dataset = hgnc_dt
  )
  ```

#### Gene symbol to aliases

  Note that this is typically a one-to-many mapping, so the result is a list instead of
  character vector.
  
  ```{r}
  crosswalk(
    c("A1BG", "A1BG-AS1", "A1CF"),
    from = "symbol",
    to = "alias_symbol",
    hgnc_dataset = hgnc_dt
  )
  ```

#### Gene symbol to locus group

  ```{r}
  # From gene symbol to locus group
  crosswalk(
    c("A1BG", "A1BG-AS1"),
    from = "symbol",
    to = "locus_group",
    hgnc_dataset = hgnc_dt
  )
  ```

#### Gene symbol to locus type

  ```{r}
  # From gene symbol to locus type
  crosswalk(
    c("A1BG", "A1BG-AS1"),
    from = "symbol",
    to = "locus_type",
    hgnc_dataset = hgnc_dt
  )
  ```

#### Gene symbol to Entrez gene id

  ```{r}
  # From gene symbol to Entrez gene id
  crosswalk(
    c("A1BG", "A1BG-AS1"),
    from = "symbol",
    to = "entrez_id",
    hgnc_dataset = hgnc_dt
  )
  ```

#### Gene symbol to Ensembl gene id

  ```{r}
  # From gene symbol to Ensembl gene id
  crosswalk(
    c("A1BG", "A1BG-AS1"),
    from = "symbol",
    to = "ensembl_gene_id",
    hgnc_dataset = hgnc_dt
  )
  ```

#### Gene symbol to MGI marker id

  ```{r}
  # From gene symbol to MGI marker id
  crosswalk(
    c("A1BG", "A1BG-AS1", "AADACL4"),
    from = "symbol",
    to = "mgd_id",
    hgnc_dataset = hgnc_dt
  )
  ```
